Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-19 manuscript.Rmd
Screwed up hIndex file.

load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")

@@

final.list <- cbind(n.so.yr, H)
final.list <- arrange(final.list, desc(n))
final.list.index <- full_join(final.list, hIndex, by = "title")

final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
    theme_bw()

>>>>

#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")

#Load required packages
library(ggplot2)
library(dplyr)
library(gridExtra)
```

@@

final.list <- cbind(n.so.yr, H)
final.list <- arrange(final.list, desc(n))
#final.list.index <- full_join(final.list, hIndex, by = "title")

#final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
#x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
#    theme_bw()
